\begin{thebibliography}{10}
	\bibitem{li2002mimo}
	Y.~Li, J.~H. Winters, and N.~R. Sollenberger, ``Mimo-ofdm for wireless
	communications: signal detection with enhanced channel estimation,''
	\emph{Communications, IEEE Transactions on}, vol.~50, no.~9, pp. 1471--1477,
	2002.
	
	\bibitem{kelly1997charging}
	F.~Kelly, ``Charging and rate control for elastic traffic,'' \emph{European
		transactions on Telecommunications}, vol.~8, no.~1, pp. 33--37, 1997.
	
	\bibitem{li2008proportional}
	L.~Li, M.~Pal, and Y.~R. Yang, ``Proportional fairness in multi-rate wireless
	lans,'' in \emph{INFOCOM 2008. The 27th Conference on Computer
		Communications. IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2008.
	
	\bibitem{li2014ap}
	W.~Li, S.~Wang, Y.~Cui, X.~Cheng, R.~Xin, M.~Al-Rodhaan, and A.~Al-Dhelaan,
	``Ap association for proportional fairness in multirate wlans,''
	\emph{Networking, IEEE/ACM Transactions on}, vol.~22, no.~1, pp. 191--202,
	2014.
	
	\bibitem{baid2012network}
	A.~Baid, M.~Schapira, I.~Seskar, J.~Rexford, and D.~Raychaudhuri, ``Network
	cooperation for client-ap association optimization,'' in \emph{Modeling and
		Optimization in Mobile, Ad Hoc and Wireless Networks (WiOpt), 2012 10th
		International Symposium on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE,
	2012, pp. 431--436.
	
	\bibitem{karimi2014optimal}
	O.~B. Karimi, J.~Liu, and J.~Rexford, ``Optimal collaborative access point
	association in wireless networks,'' in \emph{INFOCOM, 2014 Proceedings
		IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2014, pp. 1141--1149.
	
	\bibitem{gong2012ap}
	D.~Gong and Y.~Yang, ``Ap association in 802.11 n wlans with heterogeneous
	clients,'' in \emph{INFOCOM, 2012 Proceedings IEEE}.\hskip 1em plus 0.5em
	minus 0.4em\relax IEEE, 2012, pp. 1440--1448.
	
	\bibitem{yoon2013probeam}
	J.~Yoon, K.~Sundaresan, M.~A. Khojastepour, S.~Rangarajan, and S.~Banerjee,
	``Probeam: a practical multicell beamforming system for ofdma small-cell
	networks,'' in \emph{Proceedings of the fourteenth ACM international
		symposium on Mobile ad hoc networking and computing}.\hskip 1em plus 0.5em
	minus 0.4em\relax ACM, 2013, pp. 147--156.
	
	\bibitem{aryafar2010design}
	E.~Aryafar, N.~Anand, T.~Salonidis, and E.~W. Knightly, ``Design and
	experimental evaluation of multi-user beamforming in wireless lans,'' in
	\emph{Proceedings of the sixteenth annual international conference on Mobile
		computing and networking}.\hskip 1em plus 0.5em minus 0.4em\relax ACM, 2010,
	pp. 197--208.
	
	\bibitem{yoo2006optimality}
	T.~Yoo and A.~Goldsmith, ``On the optimality of multiantenna broadcast
	scheduling using zero-forcing beamforming,'' \emph{Selected Areas in
		Communications, IEEE Journal on}, vol.~24, no.~3, pp. 528--541, 2006.
	
	\bibitem{yoo2007multi}
	T.~Yoo, N.~Jindal, and A.~Goldsmith, ``Multi-antenna downlink channels with
	limited feedback and user selection,'' \emph{Selected Areas in
		Communications, IEEE Journal on}, vol.~25, no.~7, pp. 1478--1491, 2007.
	
	\bibitem{xie2014scalable}
	X.~Xie and X.~Zhang, ``Scalable user selection for mu-mimo networks,'' in
	\emph{INFOCOM, 2014 Proceedings IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax
	IEEE, 2014, pp. 808--816.
	
	\bibitem{arslan2007channel}
	H.~Arslan \emph{et~al.}, ``Channel estimation for wireless ofdm systems,''
	\emph{IEEE Surveys and Tutorials}, vol.~9, no.~2, pp. 18--48, 2007.
	
	\bibitem{blough2014interference}
	D.~M. Blough, G.~Resta, and P.~Santi, ``Interference-aware proportional
	fairness for multi-rate wireless networks,'' in \emph{INFOCOM, 2014
		Proceedings IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2014, pp.
	2733--2741.
	
	\bibitem{du2014ibeam}
	Y.~Du, E.~Aryafar, J.~Camp, and M.~Chiang, ``ibeam: Intelligent client-side
	multi-user beamforming in wireless networks,'' in \emph{INFOCOM, 2014
		Proceedings IEEE}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2014, pp.
	817--825.
	
	\bibitem{wang2014simcast}
	G.~Wang, K.~Wu, Q.~Zhang, and L.~M. Ni, ``Simcast: Efficient video delivery in
	mu-mimo wlans,'' in \emph{INFOCOM, 2014 Proceedings IEEE}.\hskip 1em plus
	0.5em minus 0.4em\relax IEEE, 2014, pp. 2454--2462.
	
	\bibitem{yu2014combating}
	H.~Yu, O.~Bejarano, and L.~Zhong, ``Combating inter-cell interference in 802.11
	ac-based multi-user mimo networks,'' in \emph{Proceedings of the 20th annual
		international conference on Mobile computing and networking}.\hskip 1em plus
	0.5em minus 0.4em\relax ACM, 2014, pp. 141--152.
	
	\bibitem{boyd2004convex}
	S.~Boyd and L.~Vandenberghe, \emph{Convex optimization}.\hskip 1em plus 0.5em
	minus 0.4em\relax Cambridge university press, 2004.
	
\end{thebibliography}